UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-11 files/paper/paper.tex
updates

\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from the true data distribution
and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$ some sense of ground truth, we also consider the $L1$
loss

@@

\subsection{Network Architecture and Training Details}
We use an encoder-decoder network similar to the work of \cite{isola2016image}, in which our generator is
structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.

``U-Net''

L1 weight 100, batch size 32, wgan loss, learning rate 1e-4, IG weight 1.0 and 0.0, 100 epochs
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.

>>>>

\noindent where $\mathbb{P}_{\hat{x}}$ is defined as samples along straight lines between pairs of points coming from the true data distribution
and the generator distribution, and $\lambda$ is a weighing factor. In order to give $G$ some sense of ground truth, as well as capture low level
frequencies in the image, we also consider the $L1$ loss

@@

\subsection{Network Architecture and Training Details}
Our generator network uses an encoder-decoder structure similar to the work of \cite{isola2016image}, which is
structured as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which this embedding is then
upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using a ``U-Net'' comes from explicitly preserving spatial
dependencies produced by the encoder, as opposed to relying on the embedding to contain all of the information. This
is done by the addition of ``skip connections'', which concatenate the activations produced from a convolution
layer $i$ in the encoder to the input of a transpose convolution layer $n-i+1$ in the decoder, where $n$ is the
total number of layers in the network. Each convolutional layer in our generator uses kernel size $4 \times 4$ with stride 2.
Following \cite{radford2015unsupervised}, we use batch normalization \cite{pmlr-v37-ioffe15} throughout except for the last layer of the decoder.

Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This is due
to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually, which batch
normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization \cite{ba2016layer},
but we found no significant improvements. RESULTS PENDING
In all of our experiments, we use $\lambda_{L1} = 100$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our implementation was done
using the Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}
